From Reversible Programs to \\ Univalent Universes and Back

### 2021-05-03 Pi+/paper/univalent.tex
Outline text in section 5
Add text in section 3.1.3

@@

\begin{definition}[Universe]
  A universe \`{a} la Tarski is given by a code $U : \UU$ and a decoding function $\El : U \to \UU$. If $\El$ is a
  univalent fibration, $U$ is a univalent universe.
\end{definition}

@@

>>>>

\begin{definition}[Propositional Truncation]
  Given a type $A$, the propositional truncation $\Trunc[-1]{A}$, or simply $\Trunc{A}$, is a higher inductive type
  generated by the following constructors,
  \begin{itemize}
    \item an inclusion function $\trunc{\blank} : A \to \Trunc{A}$,
    \item for each $x, y : \Trunc{A}$, a path $\term{trunc}(x,y) : x \id_{\Trunc{A}} y$,
  \end{itemize}
  such that, given any type $B$ with
  \begin{itemize}
    \item a function $g : A \to B$,
    \item for each $x, y : B$, a path $\term{trunc*}(x,y) : x \id_{B} y$,
  \end{itemize}
  there is a unique function $f : \Trunc{A} \to B$ such that,
  \begin{itemize}
    \item $f(\trunc{a}) \equiv g(a)$
    \item for each $x, y : \Trunc{A}$, $\ap{f}{\term{trunc}(x,y)} \id_{B} \term{trunc*}(f(x),f(y))$.
  \end{itemize}
\end{definition}

\begin{definition}[Set Quotient]
  Given a type $A$ which is an $\hSet$, and a relation $R : A \to A \to \hProp$, the set-quotient $\quot{A}{R}$ is the
  higher inductive type generated by
  \begin{itemize}
    \item an inclusion function $q : A \to \quot{A}{R}$,
    \item for each $x, y : A$ such that $R(x,y)$, a path $q(x) \id_{\quot{A}{R}} q(y)$,
    \item a set truncation, for each $x, y : \quot{A}{R}$ and $r, s : x \id_{\quot{A}{R}} y$, we have $r \id s$,
  \end{itemize}
  with an appropriate induction principle.
\end{definition}

We recall that quotients in HoTT are \emph{effective}, that is, if $R$ is an equivalence relation, we have
$R(x,y) \eqv (q(x) \id_{\quot{A}{R}} q(y))$.

@@

\begin{definition}[Universe]
  A universe \`{a} la Tarski is given by the following pieces of data,
  \begin{itemize}
    \item a code $U : \UU$,
    \item a decoding function $\El : U \to \UU$.
  \end{itemize}
  If $\El$ is a univalent fibration, $U$ is a univalent universe.
\end{definition}

@@

\begin{proof}

\end{proof}
